Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
remove 37d4cc3c530b25bf97f1052f7c187af06f832aea
Describing the parametric uncertainties results

\red{[where is this new variable used later?]}

A typical hybrid system \red{[clarify the adjective ``hybrid'']} is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$ 
\red{[this Delta term now refers to the continuous plant? this is not what has been discussed before, nor what is in some of the plots.]} 
, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.

@@

@@

Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
domain,
%
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$

@@

%------------------------------------
%\subsection{Using Fixed Point Arithmetic for verification}
%\label{fixedpoint_verification}
%------------------------------------
>>>>>>> 37d4cc3c530b25bf97f1052f7c187af06f832aea

%------------------------------------
\subsection{DSVerifier Verification Flow}
\label{verification-flow}
%------------------------------------

@@

%% \red{[clear elucidation of the mapping between this and the domains used 
%% in the general description of the synthesiser]}

\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
The {\sc synthesise} phase uses a BMC-based verifier to 
compute a solution ($N_c$,$D_C$). An important remark is that this 
controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
domain.  
\cdsay{integrate the following with Dario}
Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
using Fixed-Point bit vectors with integer size $I_b$ and fractional
size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
%
\begin{align}
\small
\label{digital_controller_plant_tf}
\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
\end{align}

The second approach uses a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program. The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples. The second phase verifies the propagation of the error in the fixed point calculations. If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution. The resulting increase in speed of this approach over the former, which is of several orders of magnitude, vouches for the use of CEGIS in most of our benchmarks.
\cdsay{end of integration}

In the {\sc verify} phase, we have a two-step process. 
First, in the {\sc Uncertainty} sub-phase, assuming the 
current precision \param{I_b}{F_b},
we check whether 
the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
If this is the case, then we obtain a counterexample denoted by 
values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which make the closed-loop system unstable. 
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $D_C$ and $N_C$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.

If the result of the {\sc Uncertainty} verification is that
the system is stable for the current candidate solution,
then we pass this solution to the {\sc Precision} verification sub-phase, 
which checks the propagation of the error in the fixed-point 
calculations. If this check returns $false$, then we 
increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase
with an empty {\sc inputs} set.
Otherwise, we found a full solution for our synthesis problem
and we are done.

\subsection{Program synthesis for the running example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with the candidate solution given below at $I_b=16,F_b=24$,
which has all coefficients 0.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

@@

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
We stay in the {\sc verify} phase and receive a new counterexample at
higher precision:
\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, i.e. 
not going back to the synthesise phase, 
then this illustration doesn't follow the general diagram in Fig.5. 
We need to decide which direction we keep.}
%
$$
\begin{array}{ll}
\Delta N_G(z) {=} 0.026314\\
\Delta D_G(z) {=} 0.999024z{-}1.004785
\end{array}
$$
%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. In the next {\sc synthesise}
phase, we get a new candidate solution that holds for the newly
inserted counterexample:

@@

@@

\begin{figure*}
\centering
\resizebox{.7\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1.5cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \node[fill=yellow!20] (synth) {{\sc Synthesise}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dashed,
	minimum width=7cm,
	minimum height=.8cm,
	label={\sc Verify},] (verif) {};
   \node[fill=yellow!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc ~Uncertainty~~~~}};
   \node[fill=yellow!20] (verif2) at ([xshift=2cm]verif.center) {{\sc ~~~~~Precision~~~}};
   } 
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \& \\
   \node (gp) {Closed-loop System Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2cm]aux.center) {BMC-based Verifier};
   \node (fp)  at ([xshift=2cm]aux.center) {Fixed-point \\Arithmetic Verifier};
   }   
    \\
  };

   \path
    ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east)
    ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
    ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south)
    (verif2) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south)
    (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2)
   ([xshift=6.7cm]aux2) edge node[align=center] {Increase Precision} (aux1);

 \end{tikzpicture}
}
 \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (CEGIS paradigm). \label{fig:CEGIS}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Evaluation}

@@

\begin{figure}[H]
\centering
\begin{tabular}{l | r r l}
Benchmark              & Base     & Unc     & \\\cline{1-4}
CruiseControl02        & 17\,s    & 46\,s   & \\
SatelliteB2            & 7\,s     & 6601\,s & \tbmark\\
SatelliteC2            & 2\,s     & 76\,s   & \tbmark\\
SpringMassDamper       & 28\,s    & \xmark  &
\end{tabular}

\vspace{0.5em}
\scriptsize{* = solved with interval back-end, \xmark = uncontrollable}
\vspace{0.5em}

>>>>

A typical hybrid system, with a continuous plant and discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$ 
, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.

@@

%------------------------------------
\subsection{Using Fixed Point Arithmetic for verification}
\label{fixedpoint_verification}
%------------------------------------

@@

@@

The second approach uses a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program. The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples. The second phase verifies the propagation of the error in the fixed point calculations. If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution. The resulting increase in speed of this approach over the former, which is of several orders of magnitude, vouches for the use of CEGIS in most of our benchmarks.
%------------------------------------
\subsection{DSVerifier Verification Flow}
\label{verification-flow}
%------------------------------------

@@

\red{[clear elucidation of the mapping between this and the domains used 
in the general description of the synthesiser]}

In the {\sc verify} phase, if the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$, 
then we obtain a counterexample denoted by 
values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which make the closed-loop system unstable. 
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $D_C$ and $N_C$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.

\paragraph{Program synthesis for the running example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with the candidate solution given below at $I_b=16,F_b=24$,
which has all coefficients 0.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

@@

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
We stay in the {\sc verify} phase and receive a new counterexample at
higher precision:
%
$$
\begin{array}{ll}
\Delta N_G(z) {=} 0.026314\\
\Delta D_G(z) {=} 0.999024z{-}1.004785
\end{array}
$$
%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. In the next {\sc synthesise}
phase, we get a new candidate solution that holds for the newly
inserted counterexample:

@@

\blue{
For the same cruise control system, the synthesis may be done considering that the plant model have parametric uncertainties ($\Delta G_{P}(z)$). Thus, the synthesised controller must to stabilize for any parametric variation $\Delta p$ inside of a given region. Specially, in this example, was assumed that each coefficient of $G(z)$ may vary $\pm 0.5\%$.
}

\blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example. Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase. The resulting controller is
}

@@

\begin{figure*}
\centering
\resizebox{.7\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1cm] {
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}}; \\
   \node[fill=yellow!20] (synth) {{\sc Synthesise}};
   \&
   \node[fill=yellow!20] (verif) {{\sc Verify}}; \\

   \& \\
   \& \\
   \node (gp) {~~~~~~~~~~~~~~Closed-loop System Search~~~~~~~~~~~~~~~};
   \&
   \node (bmc) {~~~~~~~~~~~~~~~BMC-based Verifier~~~~~~~~~~~~~~~};

    \\
  };

   \path
    ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif.west)
    ([yshift=-2em]verif.west) edge node {Counterexample} ([yshift=-2em]synth.east)
    ([xshift=5em]verif.south) edge node {Candidate $P$} ([xshift=5em]bmc.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif.south)
    (verif) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south);
 \end{tikzpicture}
}
 \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (CEGIS paradigm). \label{fig:CEGIS}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Evaluation}

@@

\begin{figure}[H]
\centering
\begin{tabular}{l | r l r l}
Benchmark              & Base     &         & Unc     & \\\cline{1-4}
CruiseControl02        & 17\,s    &         & 46\,s   & \\
SatelliteB2            & 7\,s     &         & 6601\,s & \tbmark\\
SatelliteC2            & 369\,s   & \tbmark & 76\,s   & \tbmark\\
SpringMassDamper       &          &         &         & 
\end{tabular}

\vspace{0.5em}
\scriptsize{* = solved with interval back-end}
\vspace{0.5em}
